---
title: "Day 4 Comp Session 2"
format: html
editor: visual
execute: 
  warning: FALSE
---

## 

#added a change

```{r}
library(GGally)
library(skimr)
library(palmerpenguins)

# if you don't have all these packages use install.packages
library(tidyverse)
```

## Basic Data Exploration

-   names: get variable names

-   dim: get data dimensions (rows by columns

-   head: get first n lines (6 by default)

-   tail: get last n lines (6 by default)

-   summary: get basic summary statistics

```{r}
names(penguins)

dim(penguins)

head(penguins)

tail(penguins)


#a bunch of summary statistics all at once, for each variable in the data, it gives you statistics, but it doesn't show us anything about relationships. 

summary(penguins)

#doesn't allow us to explore relationships
```

```{r}
skim(penguins)

#gives me number of missings, percent of completeness, SD, and percentiles and a histogram. 
```

We might want to look at statistics visually.

```{r}
ggpairs(penguins)

#a grid data typese to show relationships between variables among cross groups 
```

We want to practice our data visualization

## Making more exploratory charts in ggplot2

A\) Histogram

How many variables? one. it's a one variable chart

```{r}
#needs three things, ggplot, what data and variables are, what type of geom im using (chart); color is outline 

ggplot(data=penguins, aes(x= flipper_length_mm))+
  geom_histogram (fill = "blue", aes(color= species) )+
  theme_minimal()
```

```{r}
ggplot(data =penguins, aes(x= species, y= bill_length_mm))+
  geom_boxplot(fill = 'yellow', aes(color= island))+
  geom_jitter(  alpha= 0.5, aes(size = bill_depth_mm, fill = bill_depth_mm))+
  theme_dark()
```
